Comparing Facebook's Prophet Forecasting to an ARIMA Model: A Diebold-Mariano Evaluation of the Top40 Index

### 2017-09-15 template/Draft_Paper.Rmd
Typo Edits

---
# IMPORTANT: Change settings here, but DO NOT change the spacing. 
# Remove comments and add values where applicable. 
# The descriptions below should be self-explanatory
title: "Comparing Facebook Prophet Forecasts to those of an ARIMA Model"
subtitle: "A Diebold-Mariano Evaluation of the FTSE/JSE Top40 Index"
Author: "Marvelous Mubenesha"  # First Author
Student: "MBNMAR005"
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 5 # Adjust default figure sizes. This can also be done in the chunks of the text
    fig_height: 4
abstract: |
  Facebook's data science team open-sourced Prophet, a package that allows analysts to forecast a wide range of business time series at-scale. Prophet employs intensive Bayesian modelling in two tiers. Purely through MAP parameter estimation, and in a quasi-Bayesian form through an automated forecast evaluation that enables analyst to improve the model is it falls short when compared to other models. This paper assess the predictive accuracy of Prophet forecasts to those of an ARIMA model that was identified using the Box-Jenkins methodology. This is achieved through a Diebold-Mariano evaluation of rolling period forecasts of returns on the FTSE/JSE Top40 Index across daily, weekly and monthly time horizons. The results of the study suggest that there is insufficient evidence to conclude that the forecasting models have unequal predictive ability within the scope of the JSE/Top40 Index. 
---
<!-- First: Set your default preferences for chunk options: -->

@@

In business, including that involveing the stock market, analyyst ay require a large number of time series forecasts to infomr decision making.The challenge with existing reliable approaches to forecasting time series data are that the models require a considerable background in statistics to build and adapt to prevailing market conditions when needed. Several authors have recommended automatic forecasting, which are algorithms that can automatically forecast a large number of univariate time series. However, the forecasts generated by these methods have been found to be brittle as well as inflexible in allowing for prior information to be incorporated into the forecasting model [@taylor2017forecasting]. In February of 2017, Facebook's Core Datascience team open sourced ,Prophet, their time series forecasting tool whose main selling point is that it enables "forecasting-at-scale". A term coined by the data science team which is defined as, "an approach that allows a large number of analysts to forecast a large number and variety of business time series" [@taylor2017forecasting]. It has the added advantage of being less 'expensive'
than other alternatives. In addition, it is specifically prefarable over ARIMA models because of its non-linearity, flexibility and ability to accomodate varying time intervals [@taylor2017forecasting].

The objective of this paper is to compare the forecasts generated by Prophet - which uses automated, intensive Bayesian Modelling to 'forecast at scale'-, to those obtained by an ARIMA model -constructed through the Box-Jenkins methodology-,
through a Diebold-Mariano evaluation of the JSE Top40 Index. The study is particularly useful because analysts from a wide background can be able to easily forecast stock price returns, automatically and by using their prior knowledge, without a wholesome understanding of the statistical intricacies involved.

The paper is organized as follows. A review of literature relating to stock price forecasting with ARIMA models an other alternative approaches is introduced to give the reader a background into the subject matter. Thereafter, theory relating to the mathematical formulation and estimation of both the ARIMA and Prophet models is included in sections 2.2 and 2.3 respectively, to build the readers understanding of what the models look like and how they operate. Information relating to the data that was used in this study is contained in section 3, after which, the methodology used to answer the research question is described. Section 5, contains the results obtained when the methodology was executed. whilst section 6 includes a discussion of the results and how they can be interpreted to answer the research question. Lastly, the conclusion is contain in section 7 and is aimed at highlighting the main findings of the study.

# Background 
In this section we will briefly review literature that relates to the comparison of different approaches to forecasting stock returns. This will include both traditional approaches as well new methods such as automatic forecasting, machine learning techniques and quasi-Bayesian forms which incorporate analysts' prior information. The review of literature is concluded by emphasing how the findings of this paper can compliment existing research. The theoretical and mathematical formulation of an ARIMA forecasting model is  then briefly introduced. Thereafter, the theoretical framework and mathematical formulation of Facebooks' Prophet forecasting tool is discussed. Specific attention is drawn to Prophets distinguising features to give the reader an understanding of the value that this forecasting technique can potentially add to stock price prediction. Lastly, the Diebold-Mariano Evaluation technique is introduced as a method of formally testing superior predictive accuracy between two forecasting models.

@@

Artificial Neural Networks (ANNs) are a multi-layered perceptron as illustrated in  figure 1.  
![](ANN.png)  
*Figure 1 : Illustration of an Artificial neural network* [@tanikic2012artificial]  
An ANN consists of a sorted triple $(K, A, \omega)$. $K$ is a set of a multi-layered structure, V a paired set, that represents the value of the estimate in the $i^{th}$ node of the $k^{th}$ layer of the network. In Figure 1, the enlarged $a_{i,k} \in A$. Lastly, $\omega$ represents a function that defines the weights ($w_{i,r}$) of connections between neurons [@kriesel2007brief]. Artificial Neural networks apply iterated optimization of model parameters across the network in the form of weights conditional on observed values to learn [@segaran2007programming]. Several studies have compared ARIMA model forecasts to ANN and their conclusions are contradictory.

@@

The challenge of building models that generate superior stock return forecasts has led to widespread research in the field of quantitative analysis for decades, but the ARIMA modelremains the standard model against which to compare new innovations. This is because of its relative simplicity and ability to evolve into more complex applications e.g in the hybrid models considered in the literature review  
Prophet has reduced the problem of estimating a time series model to a cure fittig exercise by defining an additive, parametric function of time. The functions' parameters are then estimated using Bayesian estimation methods after which the tool automatically executes forecast evaluation to optimize its predictive ability.  
The results of this study suggest that, using a Diebold-Mariano evaluation, ARIMA and Prophet do not have a significant difference in predictive accuracy, even across time horizons of up to a month. The implications of this are that analysts can then chosse which model to use based on their needs without significantly compromising forecast  accuracy.

>>>>

---
# IMPORTANT: Change settings here, but DO NOT change the spacing. 
# Remove comments and add values where applicable. 
# The descriptions below should be self-explanatory
title: "Comparing Facebook's Prophet Forecasting to an ARIMA Model: A Diebold-Mariano Evaluation of the Top40 Index"
subtitle: "A Diebold-Mariano Evaluation of the FTSE/JSE Top40 Index"
Author: "Marvelous Mubenesha"  # First Author
Student: "MBNMAR005"
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 5 # Adjust default figure sizes. This can also be done in the chunks of the text
    fig_height: 4
abstract: |
  Facebook's data science team open-sourced Prophet, a package that allows analysts to forecast a wide range of business time series at-scale. Prophet employs intensive Bayesian modelling in two tiers. Purely through MAP parameter estimation, and in a quasi-Bayesian form through an automated forecast evaluation that enables analyst to improve the model if it falls short when compared to other models. This paper assess the predictive accuracy of Prophets' forecasts to those of an ARIMA model that was identified using the Box-Jenkins methodology. This is achieved through a Diebold-Mariano evaluation of the rolling period forecast errors of returns on the FTSE/JSE Top40 Index across daily, weekly and monthly time horizons. The results of the study suggest that there is insufficient evidence to conclude that the forecasting models have unequal predictive ability within the scope of the JSE/Top40 Index. 
---
<!-- First: Set your default preferences for chunk options: -->

@@

In business, including that involving the stock market, analysts require a large number of time series forecasts to inform decision making. The challenge with existing reliable approaches to forecasting time series data are that the models require a considerable background in statistics to build and adapt to prevailing market conditions when needed. Several authors have recommended automatic forecasting, which refers to algorithms that can automatically forecast a large number of univariate time series. However, the forecasts generated by these methods have been found to be brittle as well as inflexible in allowing for prior information to be incorporated into the forecasting model [@taylor2017forecasting]. In February of 2017, Facebook's Core Datascience team open sourced ,Prophet, their time series forecasting tool whose main selling point is that it enables "forecasting-at-scale". A term coined by the data science team which is defined as, "an approach that allows a large number of analysts to forecast a large number and variety of business time series" [@taylor2017forecasting]. It has the added advantage of being less 'expensive'
than other alternatives. In addition, it is specifically prefarable over ARIMA models because of its non-linearity, flexibility and ability to accomodate varying time intervals [@taylor2017forecasting].

The objective of this paper is to compare the rolling period forecasts generated by Prophet (which uses automated, intensive Bayesian Modelling to 'forecast-at-scale'), to those obtained by an ARIMA model (constructed through the Box-Jenkins methodology),
through a Diebold-Mariano evaluation of the JSE Top40 Index. The study is particularly useful because analysts from a wide background can automatically forecast stock price returns, and incorporate their prior knowledge in the model , without a wholesome understanding of the statistical intricacies involved.

The paper is organized as follows. A review of literature relating to stock price forecasting with ARIMA models and other alternative approaches is introduced to give the reader background information on research relating to the subject matter. Thereafter, theory relating to the mathematical formulation and estimation of both the ARIMA and Prophet models is included in sections 2.2 and 2.3 respectively, to build the readers understanding of what the models look like and how they operate. Information relating to the data that was used in this study is contained in section 3, after which, the methodology used to answer the research question is described in section 4. Section 5, contains the results obtained when the methodology was executed, whilst section 6 includes a discussion of the results and how they can be interpreted to answer the research question. Lastly, the conclusion in section 7 highlights the main findings of the study and recommends further areas of research.

# Background 
In this section we will briefly review literature that relates to the comparison of different approaches to forecasting stock returns. This will include both traditional approaches as well new methods such as automatic forecasting, machine learning techniques and quasi-Bayesian forms which incorporate analysts' prior information. The review of literature is concluded a brief introduction to the Diebold-Mariano evaluation and an outline of its suitability for the purpose of this study. The theoretical and mathematical formulation of an ARIMA forecasting model is  then briefly introduced. Thereafter, the theoretical framework and mathematical formulation of Facebooks' Prophet forecasting tool is discussed. Specific attention is drawn to Prophets distinguising features to give the reader an understanding of the value that this forecasting technique can potentially add to stock price prediction. Lastly, the Diebold-Mariano Evaluation technique is introduced as a method of formally testing superior predictive accuracy between two forecasting models.

@@

Artificial Neural Networks (ANNs) are a multi-layered perceptron as illustrated in  figure 1.  
![](ANN.png)  
*Figure 1 : Illustration of an Artificial neural network* [@tanikic2012artificial]  
An ANN consists of a sorted triple $(K, A, \omega)$. $K$ is a set representing the multiple layers/levels of the network i.e. input, hidden and output levels. A is a set of pairs that represents the value of the index of the estimate in the $i^{th}$ node of the $k^{th}$ layer of the network. In the enlarged section of Figure 1, $a_{i,k} \in A$. Lastly, $\omega$ represents a function that defines the weights ($\omega_{i,r}$) of connections between neurons [@kriesel2007brief]. Artificial Neural networks apply iterated optimization of model parameters across the network in the form of weights conditional on observed values to learn [@segaran2007programming]. Several studies have compared ARIMA model forecasts to ANN and their conclusions are contradictory.

@@

The challenge of building models that generate superior stock return forecasts has led to widespread research in the field of quantitative analysis for decades, but the ARIMA model remains the standard against which to compare new innovations. This is because of its relative simplicity and ability to evolve into more complex applications e.g in the hybrid models considered in the literature review.  
Prophet has reduced the problem of estimating a time series model to a curve fittig exercise by defining an additive, parametric function of time. The functions' parameters are then estimated using Bayesian estimation methods after which the tool automatically executes forecast evaluation to optimize its predictive ability.  
The results of this study suggest that, using a Diebold-Mariano evaluation, ARIMA and Prophet do not have a significant difference in predictive accuracy, even across time horizons of up to a month. The implications of this are that analysts can then chosse which model to use based on their needs without significantly compromising forecast  accuracy.  
This study was confined to the analysis of predictive performance during general market conditions. Further research could explore the predictive ability of the models during different market conditions.For example, performance can be compared during bull and bear market conditions or during periods of high volatility. Furthermore, research can assess whether prophet would perform better on raw data that has not been transformed, since the model is built with growth and seasonality components and could thus predict better forecasts if these features are exploited.

### 2017-09-15 template/Draft_Paper.tex
corrected notation in draft paper(P_t)
Typo Edits

\begin{center}
{\Huge \bf Comparing Facebook Prophet Forecasts to those of an ARIMA Model}\\
\today\\
Marvelous Mubenesha ( MBNMAR005)\\
{\tt MBNMAR005@uct.co.za}
\end{center}

\begin{abstract}
Facebook's data science team open-sourced Prophet, a package that allows
analysts to forecast a wide range of business time series at-scale.
Prophet employs intensive Bayesian modelling in two tiers. Purely
through MAP parameter estimation, and in a quasi-Bayesian form through
an automated forecast evaluation that enables analyst to improve the
model is it falls short when compared to other models. This paper assess
the predictive accuracy of Prophet forecasts to those of an ARIMA model
that was identified using the Box-Jenkins methodology. This is achieved
through a Diebold-Mariano evaluation of rolling period forecasts of
returns on the FTSE/JSE Top40 Index across daily, weekly and monthly
time horizons. The results of the study suggest that there is
insufficient evidence to conclude that the forecasting models have
unequal predictive ability within the scope of the JSE/Top40 Index.
\noindent
Keywords: prophet forecasting, arima forecasting, Box-Jenkins methodology,Diebold-Mariano test,multi-step rolling window forecasts, FTSE/JSE Top40 index.
\end{abstract}
\end{titlepage}

@@

In business, including that involveing the stock market, analyyst ay
require a large number of time series forecasts to infomr decision
making.The challenge with existing reliable approaches to forecasting
time series data are that the models require a considerable background
in statistics to build and adapt to prevailing market conditions when
needed. Several authors have recommended automatic forecasting, which
are algorithms that can automatically forecast a large number of
univariate time series. However, the forecasts generated by these
methods have been found to be brittle as well as inflexible in allowing
for prior information to be incorporated into the forecasting model
(Taylor and Letham 2017). In February of 2017, Facebook's Core
Datascience team open sourced ,Prophet, their time series forecasting
tool whose main selling point is that it enables
``forecasting-at-scale''. A term coined by the data science team which
is defined as, ``an approach that allows a large number of analysts to
forecast a large number and variety of business time series'' (Taylor
and Letham 2017). It has the added advantage of being less `expensive'
than other alternatives. In addition, it is specifically prefarable over
ARIMA models because of its non-linearity, flexibility and ability to
accomodate varying time intervals (Taylor and Letham 2017).

The objective of this paper is to compare the forecasts generated by
Prophet - which uses automated, intensive Bayesian Modelling to
`forecast at scale'-, to those obtained by an ARIMA model -constructed
through the Box-Jenkins methodology-, through a Diebold-Mariano
evaluation of the JSE Top40 Index. The study is particularly useful
because analysts from a wide background can be able to easily forecast
stock price returns, automatically and by using their prior knowledge,
without a wholesome understanding of the statistical intricacies
involved.

The paper is organized as follows. A review of literature relating to
stock price forecasting with ARIMA models an other alternative
approaches is introduced to give the reader a background into the
subject matter. Thereafter, theory relating to the mathematical
formulation and estimation of both the ARIMA and Prophet models is
included in sections 2.2 and 2.3 respectively, to build the readers
understanding of what the models look like and how they operate.
Information relating to the data that was used in this study is
contained in section 3, after which, the methodology used to answer the
research question is described. Section 5, contains the results obtained
when the methodology was executed. whilst section 6 includes a
discussion of the results and how they can be interpreted to answer the
research question. Lastly, the conclusion is contain in section 7 and is
aimed at highlighting the main findings of the study.

@@

In this section we will briefly review literature that relates to the
comparison of different approaches to forecasting stock returns. This
will include both traditional approaches as well new methods such as
automatic forecasting, machine learning techniques and quasi-Bayesian
forms which incorporate analysts' prior information. The review of
literature is concluded by emphasing how the findings of this paper can
compliment existing research. The theoretical and mathematical
formulation of an ARIMA forecasting model is then briefly introduced.
Thereafter, the theoretical framework and mathematical formulation of
Facebooks' Prophet forecasting tool is discussed. Specific attention is
drawn to Prophets distinguising features to give the reader an
understanding of the value that this forecasting technique can
potentially add to stock price prediction. Lastly, the Diebold-Mariano
Evaluation technique is introduced as a method of formally testing
superior predictive accuracy between two forecasting models.

@@

Artificial Neural Networks (ANNs) are a multi-layered perceptron as
illustrated in figure 1.\\
\includegraphics{ANN.png}\\
\emph{Figure 1 : Illustration of an Artificial neural network} (Tanikic
and Despotovic 2012)\\
An ANN consists of a sorted triple \((K, A, \omega)\). \(K\) is a set of
a multi-layered structure, V a paired set, that represents the value of
the estimate in the \(i^{th}\) node of the \(k^{th}\) layer of the
network. In Figure 1, the enlarged \(a_{i,k} \in A\). Lastly, \(\omega\)
represents a function that defines the weights (\(w_{i,r}\)) of
connections between neurons (Kriesel 2007). Artificial Neural networks
apply iterated optimization of model parameters across the network in
the form of weights conditional on observed values to learn (Segaran
2007). Several studies have compared ARIMA model forecasts to ANN and
their conclusions are contradictory.

@@

In this paper, the \textbf{log return}(which will be used
interchangeably with \textbf{return}), over the period \([t,t+1]\) is
denoted by \(r_t\), and was calculated by evaluating;\\
\[
r_t = log(\frac{P_{t+1}}{P_t})  \label{eq1}
\]\\
Where \(P_{t+1}\) and \(P_{t+1}\) represent the price of the index at
time \(t\) and \(t+1\) respectively.

@@

The challenge of building models that generate superior stock return
forecasts has led to widespread research in the field of quantitative
analysis for decades, but the ARIMA modelremains the standard model
against which to compare new innovations. This is because of its
relative simplicity and ability to evolve into more complex applications
e.g in the hybrid models considered in the literature review\\
Prophet has reduced the problem of estimating a time series model to a
cure fittig exercise by defining an additive, parametric function of
time. The functions' parameters are then estimated using Bayesian
estimation methods after which the tool automatically executes forecast
evaluation to optimize its predictive ability.\\
The results of this study suggest that, using a Diebold-Mariano
evaluation, ARIMA and Prophet do not have a significant difference in
predictive accuracy, even across time horizons of up to a month. The
implications of this are that analysts can then chosse which model to
use based on their needs without significantly compromising forecast
accuracy.

>>>>

\begin{center}
{\Huge \bf Comparing Facebook's Prophet Forecasting to an ARIMA Model: A
Diebold-Mariano Evaluation of the Top40 Index}\\
\today\\
Marvelous Mubenesha ( MBNMAR005)\\
{\tt MBNMAR005@uct.co.za}
\end{center}

\begin{abstract}
Facebook's data science team open-sourced Prophet, a package that allows
analysts to forecast a wide range of business time series at-scale.
Prophet employs intensive Bayesian modelling in two tiers. Purely
through MAP parameter estimation, and in a quasi-Bayesian form through
an automated forecast evaluation that enables analyst to improve the
model if it falls short when compared to other models. This paper assess
the predictive accuracy of Prophets' forecasts to those of an ARIMA
model that was identified using the Box-Jenkins methodology. This is
achieved through a Diebold-Mariano evaluation of the rolling period
forecast errors of returns on the FTSE/JSE Top40 Index across daily,
weekly and monthly time horizons. The results of the study suggest that
there is insufficient evidence to conclude that the forecasting models
have unequal predictive ability within the scope of the JSE/Top40 Index.
\noindent
Keywords: prophet forecasting, arima forecasting, Box-Jenkins methodology,Diebold-Mariano test,multi-step rolling window forecasts, FTSE/JSE Top40 index.
\end{abstract}
\end{titlepage}

@@

In business, including that involving the stock market, analysts require
a large number of time series forecasts to inform decision making. The
challenge with existing reliable approaches to forecasting time series
data are that the models require a considerable background in statistics
to build and adapt to prevailing market conditions when needed. Several
authors have recommended automatic forecasting, which refers to
algorithms that can automatically forecast a large number of univariate
time series. However, the forecasts generated by these methods have been
found to be brittle as well as inflexible in allowing for prior
information to be incorporated into the forecasting model (Taylor and
Letham 2017). In February of 2017, Facebook's Core Datascience team open
sourced ,Prophet, their time series forecasting tool whose main selling
point is that it enables ``forecasting-at-scale''. A term coined by the
data science team which is defined as, ``an approach that allows a large
number of analysts to forecast a large number and variety of business
time series'' (Taylor and Letham 2017). It has the added advantage of
being less `expensive' than other alternatives. In addition, it is
specifically prefarable over ARIMA models because of its non-linearity,
flexibility and ability to accomodate varying time intervals (Taylor and
Letham 2017).

The objective of this paper is to compare the rolling period forecasts
generated by Prophet (which uses automated, intensive Bayesian Modelling
to `forecast-at-scale'), to those obtained by an ARIMA model
(constructed through the Box-Jenkins methodology), through a
Diebold-Mariano evaluation of the JSE Top40 Index. The study is
particularly useful because analysts from a wide background can
automatically forecast stock price returns, and incorporate their prior
knowledge in the model , without a wholesome understanding of the
statistical intricacies involved.

The paper is organized as follows. A review of literature relating to
stock price forecasting with ARIMA models and other alternative
approaches is introduced to give the reader background information on
research relating to the subject matter. Thereafter, theory relating to
the mathematical formulation and estimation of both the ARIMA and
Prophet models is included in sections 2.2 and 2.3 respectively, to
build the readers understanding of what the models look like and how
they operate. Information relating to the data that was used in this
study is contained in section 3, after which, the methodology used to
answer the research question is described in section 4. Section 5,
contains the results obtained when the methodology was executed, whilst
section 6 includes a discussion of the results and how they can be
interpreted to answer the research question. Lastly, the conclusion in
section 7 highlights the main findings of the study and recommends
further areas of research.

@@

In this section we will briefly review literature that relates to the
comparison of different approaches to forecasting stock returns. This
will include both traditional approaches as well new methods such as
automatic forecasting, machine learning techniques and quasi-Bayesian
forms which incorporate analysts' prior information. The review of
literature is concluded a brief introduction to the Diebold-Mariano
evaluation and an outline of its suitability for the purpose of this
study. The theoretical and mathematical formulation of an ARIMA
forecasting model is then briefly introduced. Thereafter, the
theoretical framework and mathematical formulation of Facebooks' Prophet
forecasting tool is discussed. Specific attention is drawn to Prophets
distinguising features to give the reader an understanding of the value
that this forecasting technique can potentially add to stock price
prediction. Lastly, the Diebold-Mariano Evaluation technique is
introduced as a method of formally testing superior predictive accuracy
between two forecasting models.

@@

Artificial Neural Networks (ANNs) are a multi-layered perceptron as
illustrated in figure 1.\\
\includegraphics{ANN.png}\\
\emph{Figure 1 : Illustration of an Artificial neural network} (Tanikic
and Despotovic 2012)\\
An ANN consists of a sorted triple \((K, A, \omega)\). \(K\) is a set
representing the multiple layers/levels of the network i.e.~input,
hidden and output levels. A is a set of pairs that represents the value
of the index of the estimate in the \(i^{th}\) node of the \(k^{th}\)
layer of the network. In the enlarged section of Figure 1,
\(a_{i,k} \in A\). Lastly, \(\omega\) represents a function that defines
the weights (\(\omega_{i,r}\)) of connections between neurons (Kriesel
2007). Artificial Neural networks apply iterated optimization of model
parameters across the network in the form of weights conditional on
observed values to learn (Segaran 2007). Several studies have compared
ARIMA model forecasts to ANN and their conclusions are contradictory.

@@

In this paper, the \textbf{log return}(which will be used
interchangeably with \textbf{return}), over the period \([t,t+1]\) is
denoted by \(r_t\), and was calculated by evaluating;\\
\[
r_t = log(\frac{P_{t+1}}{P_t})  \label{eq1}
\]\\
Where \(P_t\) and \(P_{t+1}\) represent the price of the index at time
\(t\) and \(t+1\) respectively.

@@

The challenge of building models that generate superior stock return
forecasts has led to widespread research in the field of quantitative
analysis for decades, but the ARIMA model remains the standard against
which to compare new innovations. This is because of its relative
simplicity and ability to evolve into more complex applications e.g in
the hybrid models considered in the literature review.\\
Prophet has reduced the problem of estimating a time series model to a
curve fittig exercise by defining an additive, parametric function of
time. The functions' parameters are then estimated using Bayesian
estimation methods after which the tool automatically executes forecast
evaluation to optimize its predictive ability.\\
The results of this study suggest that, using a Diebold-Mariano
evaluation, ARIMA and Prophet do not have a significant difference in
predictive accuracy, even across time horizons of up to a month. The
implications of this are that analysts can then chosse which model to
use based on their needs without significantly compromising forecast
accuracy.\\
This study was confined to the analysis of predictive performance during
general market conditions. Further research could explore the predictive
ability of the models during different market conditions.For example,
performance can be compared during bull and bear market conditions or
during periods of high volatility. Furthermore, research can assess
whether prophet would perform better on raw data that has not been
transformed, since the model is built with growth and seasonality
components and could thus predict better forecasts if these features are
exploited.
